MP MetaAnalysis

### 2018-12-03 Paper_Analyses.Rmd
Comments, now in rmd

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r Setup, echo = FALSE, warning=FALSE, warning = FALSE, error = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, tidy = TRUE, message = FALSE, error = FALSE)

@@

full_estimate <- function(x) paste0(" = ", r2(x$estimate), ", SE = ", r2(x$se), ", 95% CI[",  r2(x$ci.lb), ", ", r2(x$ci.ub),"], *p*", psig(x$pval))

# moderator test
mod_test <- function(x) paste0("QM(", r2(x$m), ") = ", r2(x$QM), ", *p*", psig(x$QMp))

@@

@@

@@

#remove outliers, for now we have none, though
db_ET_MP$nooutlier = ifelse(db_ET_MP$g_calc > mean(db_ET_MP$g_calc, na.rm = TRUE) + 3*sd(db_ET_MP$g_calc, na.rm = TRUE) 
                         | db_ET_MP$g_calc < mean(db_ET_MP$g_calc, na.rm = TRUE) - 3*sd(db_ET_MP$g_calc, na.rm = TRUE),FALSE, TRUE)
db_ET_MP = db_ET_MP[db_ET_MP$nooutlier,]

db_ET_correct$nooutlier = ifelse(db_ET_correct$g_calc > mean(db_ET_correct$g_calc, na.rm = TRUE) + 3*sd(db_ET_correct$g_calc, na.rm = TRUE) 
                         | db_ET_correct$g_calc < mean(db_ET_correct$g_calc, na.rm = TRUE) - 3*sd(db_ET_correct$g_calc, na.rm = TRUE),FALSE, TRUE)
db_ET_correct = db_ET_correct[db_ET_correct$nooutlier,]

@@

#Themes and plot
apatheme=theme_bw()+
  theme(panel.grid.major=element_blank(),
    panel.grid.minor=element_blank(),
    panel.border=element_blank(),
    axis.line=element_line(),
    text=element_text(family='Times', size=25))

@@

@@

[Christina: changed concepts to mechanisms in the next paragraph, because I want to refer to what they represent, but I am not sure it's the right term]
[Katie: Karen (Mulak) talks about these terms as concepts. Mechanisms to me means some sort of internalization, that they would have had this ability all along and just need to apply it. It could be that we fundamentally disagree on this, but to me these are things that infants discover. Later on we use principles. What about "principles that infants must discover"... "in order to form adult-like word representations"? I took away "which are both present in the mature language processing system".]

@@

[Katie: since we actually don't have theoretical framework support for the no-change theory, I've changed around the sentence below to explicitly say that only 2 of the 3 are predicted by theoretical accounts.]

@@

dat_st <- dat

Sum_table <- dat_st %>%
      group_by(short_cite) %>% 
      summarise(Publication = unique(publication_status),
        Ages_Tested_months = paste(unique(trunc(mean_age_1/30.34)), collapse=', '),
                Vocabulary = ifelse(all(is.na(r_comprehension)) & all(is.na(r_production)), "None",
                                ifelse(!all(is.na(r_comprehension)) & !all(is.na(r_production)), "Comp/Prod",
                                       ifelse(!all(is.na(r_comprehension)) & all(is.na(r_production)), "Comp", "Prod"))))

@@

```
[Christina] I've shortened the labels and wanted to try out apa_table
[Katie] I like the idea, but does it work for you? It doesn't work for me...
[Katie] We have it currently set at less than 31 months, not 36, so I've changed below.

We first generated a list of potentially relevant items to be included in our meta-analysis by creating an expert list. This process yielded 110 items. We then used the google scholar search engine to search for papers citing the original Swingley & Aslin (2000) publication. This search was conducted on 22 September, 2017 and yielded 288 results. We screened the resulting 398 items, removing 99 duplicate items. We screened remaining 299 items for their title and abstract to determine whether it met the following inclusion criteria: (1) original data was reported; (2) the experiment examined familiar word recognition and mispronunciations; (3) infants studied were under 31-months-of-age; (4) the dependent variable was derived from proportion of looks to a target image versus a distractor in a eye movement experiment; (5) the stimuli were auditory speech. The final sample (n = *`r length(unique(dat$short_cite))`*) consisted of `r with(dat, n_distinct(short_cite[publication_status == "paper"]))` journal articles, `r with(dat, n_distinct(short_cite[publication_status == "proceedings"]))` proceedings paper, `r with(dat, n_distinct(short_cite[publication_status == "dissertation"]))` thesis, and `r with(dat, n_distinct(short_cite[publication_status == "gray paper"]))` unpublished reports. We will refer to these items collectively as papers. Table 1 (Summary Table) provides an overview of all papers included in the present meta-analysis.

@@

The `r length(unique(dat$short_cite))` papers we identified as relevant were then coded with as much consistently reported detail as possible (Tsuji, Bergmann, & Cristia, 2014; Bergmann et al., 2018). For each experiment (note that a paper typically has multiple experiments), we entered variables describing the publication, population, experiment design and stimuli, and results. For the analyses presented in this section, we focus on the following characteristics:

@@

We separated conditions according to whether or not the target word was mispronounced to be able to investigate infants' looking to the target picture as well as their mispronunciation sensitivity, which is the difference between looks to the target in correct and mispronounced trials. When the same infants were further exposed to multiple mispronunciation conditions and the results were reported separately in the paper, we also entered each condition as a separate row  (e.g., consonant versus vowel mispronunciations; Mani & Plunkett, 2007).  The fact that the same infants contributed data to multiple rows (minimally those containing information on correct and mispronounced trials) leads to shared variance across effect sizes, which we account for in our analyses (see next section). We will call each row a record; in total there were `r nrow(dat)` records in our data.

@@

es_info <- dat %>%
  group_by(es_method) %>%
  summarize(n_unique = n_distinct(short_cite), count = n())

corr_info <- dat %>%
  group_by(imputed_corr) %>%
  summarize(n_unique = n_distinct(short_cite), count = n())

```
[Christina] I think it would be useful to say how many records, not papers, report each measure. e.g. "(n = xxx records from yyy papers)". Would that be ok?
[Katie] Totally! I think that gives a good bit of information. Good suggestion!

@@

[Christina] Katie, do you know whether the difference is computed based on items, participants, trials...? Is there consistency?
[Katie] From working with Nivi, we did it participants x condition or participants x trial (but mostly the former). But, this is not something we reported in papers. I don't think I read it at all when putting together the dataset for this either.

@@

[Christina] These numbers seem wrong! Again, how about (xx effect sizes from yy papers)?
[Katie] Well, they are kind of wrong :) Two papers report both for different experimental conditions. I've given the explanation now, not sure if that is good enough, but I'm really not sure how to say it a different way.
[Katie] Do you want number of records and papers for the imputed correlations as well? You've put a -1, assuming there was something wrong with one of the papers or something like that? How does that shake out for number of records?

We calculated Hedges' *g* using the raw means and standard deviations reported in the paper (*n* = `r with(es_info, sum(count[es_method == "group_means_one" | es_method == "group_means_two"]))` records from `r with(es_info, sum(n_unique[es_method == "group_means_one" | es_method == "group_means_two"]))` papers) or using reported t-values (*n* = `r with(es_info, sum(count[es_method == "t_one" | es_method == "t_two"]))` records from `r with(es_info, sum(n_unique[es_method == "t_one" | es_method == "t_two"]))` papers). Two papers reported raw means and standard deviations for some experimental conditions and just t-values for the remaining experimental conditions (Swingley, 2016; Altvater-Mackensen et al., 2014). Raw means and standard deviations were extracted from figures for `r with(dat, n_distinct(short_cite[ x_from_graph == "yes"]))` papers. In a within-participation design, when two means are compared (i.e. looking during pre- and post-naming) it is necessary to obtain correlations between the two measurements at the participant level to calculate effect sizes and effect size variance based on t-values. Upon request we were provided with correlation values for one paper (Altvater-Mackensen, 2010); we were able to compute correlations using means, standard deviations, and t-values for *n* = `r with(corr_info, n_unique[imputed_corr == "no"]) - 1` (following Csibra, et al. 2016, Appendix B; see also Rabagliati, Ferguson, & Lew-Williams, 2018). Correlations were imputed for the remaining papers (see Black & Bergmann, 2017, for the same procedure). We could compute a total of `r sum(dat$is_mp == 0)` effect sizes for correct pronunciations and `r sum(dat$is_mp == 1)` for mispronunciations.

@@

Second, we analyze all of the significant results in the dataset using a p-curve from the p-curve app (v4.0, p-curve.com; @pcurve). This p-curve tests for evidential value by examining whether the p-values follow the expected distribution of a right skew in case the alternative hypothesis is true, versus a flat distribution that speaks for no effect being present in the population and all significant effect being spurious. 
Responses to correctly pronounced and mispronounced labels are predicted to show different patterns of looking behavior. In other words, there is an expectation that infants should look to the target when hearing a correct pronunciation, but some studies may report either significant looks or no  significant looks to the target when hearing a mispronounced label

[Christina] Katie, is that right, can you add a citation? 
[Katie] I've rewritten it a bit to be explicit about the difference between expectations for correct and mispronounced labels. I'm not sure what to cite though. The papers that find significant looks or no significant looks? That's basically the meta-analysis. Or some citation that talks about what looking to the target upon hearing a mispronunciation means in comparison to what target looks being decreased for mispronunciations relative to correct pronunciations means? I'm not so sure whether anyone has actually talked about that difference before, not sure what to cite.

(i.e. there might be no effect present in the population, see e.g., ); as a result, we conduct these two analyses to assess publication bias separately for both conditions.

@@

@@

We should also point out that funnel plot asymmetry can be caused by multiple factors beside publication bias. The funnel plot asymmetry may also reflect heterogeneity in the data. There are various possible sources of heterogeneity, which our subsequent moderator analyses will begin to address. Nonetheless, we will remain cautious in our interpretation of our findings and hope that an open dataset that can be expanded by the community will attract previously unpublished null results so we can better understand infants' developing mispronunciation sensitivity.

@@

We first calculated the meta-analytic effect for infants' ability to identify objects when hearing correctly pronounced labels. The variance-weighted meta-analytic effect size Hedges' *g* was `r g_SE(sum_eff)` which was significantly different from zero `r CI_p(sum_eff)`. This is a rather large effect size (according to the criteria set by Cohen, 1988; see also Bergmann, et al., 2018; for comparative meta-analytic effect sizes in language acquisition research). That the effect size is significantly above zero suggests that when presented with the correctly pronounced label, infants fixated the corresponding object. Our analysis of funnel plot asymmetry, however, found evidence for publication bias, which might lead to an overestimated effect sizes as smaller, non-significant results might not be published despite the fact that they should occur regularly even in well-powered studies. Although the effect size Hedges' *g* may be overestimated for object identification in response to correctly pronounced words, the p-curve results and a CI lower bound of `r r2(sum_eff$ci.lb)` which is substantially above zero suggests that this result should be robust even when correcting for publication bias. In other words, we are confident that the true population mean lies above zero for object recognition of correctly pronounced words.

@@

[Christina] I am not sure about the placement of this paragraph because the next section cannot explain this heterogeneity, so maybe we should move it down to the beginning of the age part?
[Katie] I think that makes sense, moving it!

@@

To evaluate the different predictions we laid out in the introduction for how mispronunciation sensitivity will change as infants develop, we next added the moderator age (centered; continuous and measured in days but transformed into months for ease of interpreting estimates by dividing by 30.44 for Figure 2). 
[Christina] What about the whole months thing?
[Katie] We had an explanation in the methods section for this, I've now added it again here.

@@

[Christina] OK there is a mismatch between what you write and the numbers, can you verify?
[Katie] Good catch. For some reason, it was just copying over the moderator test from mispronunciation sensitivity, even though I was calling for the age moderator analysis. There is no significant moderator test, but it was just pasting the same one again and again. I've fixed my code, so it should be correct now!

@@

We then examined the interaction between age and mispronunciation sensitivity (correct vs. mispronounced words) in our whole dataset. The moderator test was significant (`r mod_test(rma_MPeffect_age)`). The interaction between age and mispronunciation sensitivity, however, was not significant ($\beta$ `r full_estimate(sum_eff)`), pointing to the moderator test being driven by the difference between conditions. The small estimate, as well as inspection of Figure 2 suggests that as infants age, their mispronunciation sensitivity remains the same.

@@

@@

p.diff <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity)) + 
  ggtitle("b. Mispronunciation Sensitivity")+
  geom_point(aes(size = n_1/2),show.legend=FALSE, alpha = .3) + 
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1), color = "black") +
  scale_colour_manual(values=cbPalette)+
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Mispronunciation Sensitivity")

@@

Of the `r n_distinct(dat$short_cite)` papers included in the meta-analysis, `r with(vi2, papers[has_vocab == "vocab"])` analyzed the relationship between vocabulary scores and object recognition for correct pronunciations and mispronunciations (comprehension = `r with(vi1, papers[has_vocab == "comprehension"])` papers and `r with(vi1, count[has_vocab == "comprehension"])` records; production = `r with(vi1, papers[has_vocab == "production"])` papers and `r with(vi1, count[has_vocab == "production"])` records). There is reason to believe that production data are different from comprehension data (the former being easier to estimate for parents in the typical questionnaire-based assessment; Kidd citation), and we therefore planned to analyze these two types of vocabulary measurement separately. However, only `r with(vi1, papers[has_vocab == "production"])` papers reported correlations with productive vocabulary scores, limiting the conclusions that can be drawn. In our vocabulary analysis, we therefore focus exclusively on the relationship between comprehension and mispronunciation sensitivity.

[Christina] Removed the previous comment chaos.
So can you not only list papers but also n conditions above? With just 1 paper for production, I wouldn't analyze it to be honest. it's just not enough data. 
I also liked your comments about the time line of this whole thing, can you extract the years of papers which report this? Might be extremely useful in the discussion and strengthens our case that there is no effect, bc people don't find the predicted relation with vocab. 
Also, cann you add a citation for comp vs prod? I think Evan Kidd had a paper on it, if you don't have one handy, I can look it up.
[Katie] I couldn't find what you are referring to. Could you add the Evan Kidd paper? Also, I added a histogram figure below, but I'm not so very sure that it is good enough to add to the paper (its under the heading "Potential Vocabulary Figure"). Let me know what you think.

@@

@@

[Christina] Is there a reason you choose mode and not median? 
[Katie] Hmm, I felt like mode would be interesting, because it gives the most popular choice (74 experimental conditions). But, the median is only 500 ms less, so we could use that too (9 experimental conditions).

[Christina] Would it make sense to present dependent variable first? 
[Katie] I don't have a strong opinion on this. If you think it would be better, then I can change it.

@@

[Christina] The canfield & haith paper is for visual stimuli, right? So add that before "stimulus". And then add to the next sentence that the longer latnecies are because ther eis addiitonal language processing required which EEg shows in adults to take X ms (400 for N400?). 
[Katie] I agree with the reasoning, but I don't think referring to adult ERP literature is the way to go. I've rewritten these sentences to be more faithful to the misp sensitivity literature.

[Christina] Can you add info how many papers did not report the analyzed variables? Across this whole section, I mean. 
[Katie] All papers reported the actual post-naming phase length and the size of the post-naming time window analyzed.

@@

[Christina] I think it's a bit inconsistent whether it's post naming phase or window, how about window? Phase sounds wrong to me. or analysis window? I also find phase size odd, and again prefer window (window size). Your call though. 
[Katie] I agree and I've updated it to refer to window size when talking about the analyzed portion and to  phase when refering to it as the entire actual presentation time.

@@

@@

p.AGE <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity, color = post_size)) + 
    #facet_grid(.~post_size)+
  geom_point(aes(size = n_1),show.legend=FALSE) +
  labs(title="b")+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1)) +
  scale_colour_manual(values=cbPalette)+
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Misp. Sensitivity")

@@

[Christina] Generally, it might be easier to kick out all object recognition analyses (what do they tell us?) and start out that we only analyze MP sensitivity, i.e. consider the whole dataset and always include condition as moderator. 
[Katie] Agreed! I've gotten rid of all of the object recognition analyses and added an explanation at the beginning of the Exploratory Analysis section.

@@

[Christina] Did I ask the following already: Do we know whether subtrations were on the trial level? Pre vs post is a bit differnt because it loses the individual bias accommodation and the correlation between pre and post on the participant / item level. 
[Katie] You did. I'll put here my answer from before:
From working with Nivi, we did it participants x condition or participants x trial (but mostly the former). But, this is not something we reported in papers. I don't think I read it at all when putting together the dataset for this either.

>>>>

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_word
---

```{r Setup, echo = FALSE, warning=FALSE, error = FALSE, message = FALSE, tidy = TRUE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, tidy = TRUE, message = FALSE, error = FALSE)

@@

full_estimate <- function(x) paste0(" = ", r2(x$estimate), ", SE = ", r2(x$se), ", 95% CI[",  r2(x$ci.lb), ", ", r2(x$ci.ub),"], *p* ", psig(x$pval))

# moderator test
mod_test <- function(x) paste0("QM(", r2(x$m), ") = ", r2(x$QM), ", *p* ", psig(x$QMp))

@@

noES <- db_ET %>%
  filter(is.na(d_calc)) %>%
  group_by(short_cite) %>%
  summarise(n_records = n())

@@

descriptive_dat <- db_ET

db_ET <- db_ET %>%
  filter(!is.na(d_calc))

@@

#remove outliers
db_ET_MP$nooutlier = ifelse(db_ET_MP$g_calc > mean(db_ET_MP$g_calc, na.rm = TRUE) + 3*sd(db_ET_MP$g_calc, na.rm = TRUE) 
                         | db_ET_MP$g_calc < mean(db_ET_MP$g_calc, na.rm = TRUE) - 3*sd(db_ET_MP$g_calc, na.rm = TRUE),FALSE, TRUE)

n_outlier_MP = sum(db_ET_MP$nooutlier==FALSE)

db_ET_MP = db_ET_MP[db_ET_MP$nooutlier,]

# 3 outliers

db_ET_correct$nooutlier = ifelse(db_ET_correct$g_calc > mean(db_ET_correct$g_calc, na.rm = TRUE) + 3*sd(db_ET_correct$g_calc, na.rm = TRUE) 
                         | db_ET_correct$g_calc < mean(db_ET_correct$g_calc, na.rm = TRUE) - 3*sd(db_ET_correct$g_calc, na.rm = TRUE),FALSE, TRUE)

n_outlier_correct = sum(db_ET_correct$nooutlier==FALSE)

db_ET_correct = db_ET_correct[db_ET_correct$nooutlier,]

# 2 outliers

@@

#Themes and plot
apatheme=theme_bw()+
  theme(panel.grid.major=element_blank(),
    panel.grid.minor=element_blank(),
    panel.border=element_blank(),
    axis.line=element_line()#,
    #text=element_text(family='Times', size=25)
    )

@@

[Christina: Big change: I just realized that we also need to report where we could not compute effect sizes, added this info. ]

@@

[Christina: changed concepts to mechanisms in the next paragraph, because I want to refer to what they represent, but I am not sure it's the right term]
[Katie: Karen (Mulak) talks about these terms as concepts. Mechanisms to me means some sort of internalization, that they would have had this ability all along and just need to apply it. It could be that we fundamentally disagree on this, but to me these are things that infants discover. Later on we use principles. What about "principles that infants must discover"... "in order to form adult-like word representations"? I took away "which are both present in the mature language processing system".]
[Christina: I like principles. This is then good for me.]

@@

[Katie: since we actually don't have theoretical framework support for the no-change theory, I've changed around the sentence below to explicitly say that only 2 of the 3 are predicted by theoretical accounts.]
[Christina: Works for me. I am just thinking what the Vihman-style framework says. do you happen to know? I think the Renner thesis discusses it.]

@@

dat_st <- descriptive_dat

Sum_table <- dat_st %>%
      group_by(short_cite) %>% 
      summarise(Publication = unique(publication_status),
        Ages_Tested_months = paste(unique(trunc(mean_age_1/30.44)), collapse=', '),
                Vocabulary = ifelse(all(is.na(r_comprehension)) & all(is.na(r_production)), "None",
                                ifelse(!all(is.na(r_comprehension)) & !all(is.na(r_production)), "Comp/Prod",
                                       ifelse(!all(is.na(r_comprehension)) & all(is.na(r_production)), "Comp", "Prod"))))

@@

[Christina] I've shortened the labels and wanted to try out apa_table
[Katie] I like the idea, but does it work for you? It doesn't work for me...
[Katie] We have it currently set at less than 31 months, not 36, so I've changed below.

[Christina: OK to age. Apa table works for me, weird. It should come with papaja. Might be related to the issues you have wrt to citations? ]
[Christina: Suggestions re: table. Add N effect sizes? you cna do it with summarise(number_ES = n()) I think]
[Christina: Btw, I think I've corrected short_cite in the online spreadsheet, so the table should be fine now.]

We first generated a list of potentially relevant items to be included in our meta-analysis by creating an expert list. This process yielded 110 items. We then used the google scholar search engine to search for papers citing the original Swingley & Aslin (2000) publication. This search was conducted on 22 September, 2017 and yielded 288 results. We removed 99 duplicate items and screened the remaining 299 items for their title and abstract to determine whether each met the following inclusion criteria: (1) original data was reported; (2) the experiment examined familiar word recognition and mispronunciations; (3) infants studied were under 31-months-of-age and typically developing; (4) the dependent variable was derived from proportion of looks to a target image versus a distractor in a eye movement experiment; (5) the stimuli were auditory speech. The final sample (n = *`r length(unique(descriptive_dat$short_cite))`*) consisted of `r with(descriptive_dat, n_distinct(short_cite[publication_status == "paper"]))` journal articles, `r with(descriptive_dat, n_distinct(short_cite[publication_status == "proceedings"]))` proceedings paper, `r with(descriptive_dat, n_distinct(short_cite[publication_status == "dissertation"]))` thesis, and `r with(descriptive_dat, n_distinct(short_cite[publication_status == "gray paper"]))` unpublished reports. We will refer to these items collectively as papers. Table 1 (Summary Table) provides an overview of all papers included in the present meta-analysis.

@@

The `r length(unique(descriptive_dat$short_cite))` papers we identified as relevant were then coded with as much consistently reported detail as possible (Tsuji, Bergmann, & Cristia, 2014; Bergmann et al., 2018). For each experiment (note that a paper typically has multiple experiments), we entered variables describing the publication, population, experiment design and stimuli, and results. For the analyses presented in this section, we focus on the following characteristics:

@@

We separated conditions according to whether or not the target word was mispronounced to be able to investigate infants' looking to the target picture as well as their mispronunciation sensitivity, which is the difference between looks to the target in correct and mispronounced trials. When the same infants were further exposed to multiple mispronunciation conditions and the results were reported separately in the paper, we also entered each condition as a separate row  (e.g., consonant versus vowel mispronunciations; Mani & Plunkett, 2007).  The fact that the same infants contributed data to multiple rows (minimally those containing information on correct and mispronounced trials) leads to shared variance across effect sizes, which we account for in our analyses (see next section). We will call each row a record; in total there were `r nrow(descriptive_dat)` records in our data.

@@

es_info <- descriptive_dat %>%
  filter(!is.na(d_calc)) %>%
  group_by(es_method) %>%
  summarize(n_unique = n_distinct(short_cite), count = n())

corr_info <- descriptive_dat %>%
  filter(!is.na(d_calc)) %>%
  group_by(imputed_corr) %>%
  summarize(n_unique = n_distinct(short_cite), count = n())

[Christina: I needed to move this around because we first need to say that we could not compute some effect sizes and removed outlierts.]

[Christina] These numbers seem wrong! Again, how about (xx effect sizes from yy papers)?
[Katie] Well, they are kind of wrong :) Two papers report both for different experimental conditions. I've given the explanation now, not sure if that is good enough, but I'm really not sure how to say it a different way.
[Katie] Do you want number of records and papers for the imputed correlations as well? You've put a -1, assuming there was something wrong with one of the papers or something like that? How does that shake out for number of records?
[Christina: No clue what the -1 was, sorry.]

We calculate Hedges' *g* using the raw means and standard deviations reported in the paper (*n* = `r with(es_info, sum(count[es_method == "group_means_one" | es_method == "group_means_two"]))` records from `r with(es_info, sum(n_unique[es_method == "group_means_one" | es_method == "group_means_two"]))` papers) or using reported t-values (*n* = `r with(es_info, sum(count[es_method == "t_one" | es_method == "t_two"]))` records from `r with(es_info, sum(n_unique[es_method == "t_one" | es_method == "t_two"]))` papers). Two papers reported raw means and standard deviations for some experimental conditions and just t-values for the remaining experimental conditions (Swingley, 2016; Altvater-Mackensen et al., 2014). Raw means and standard deviations were extracted from figures for `r with(descriptive_dat, n_distinct(short_cite[ x_from_graph == "yes"]))` papers. In a within-participation design, when two means are compared (i.e. looking during pre- and post-naming) it is necessary to obtain correlations between the two measurements at the participant level to calculate effect sizes and effect size variance based on t-values. Upon request we were provided with correlation values for one paper (Altvater-Mackensen, 2010); we were able to compute correlations using means, standard deviations, and t-values for *n* = `r with(corr_info, n_unique[imputed_corr == "no"])` (following Csibra, et al. 2016, Appendix B; see also Rabagliati, Ferguson, & Lew-Williams, 2018). Correlations were imputed for the remaining papers (see Black & Bergmann, 2017, for the same procedure). For two papers, we could not derive any effect size (Ballem & Plunkett, Renner), and for a third paper, we do not have sufficient information in one record to compute effect sizes (Skoruppa). We compute a total of `r sum(dat$is_mp == 0)+n_outlier_correct` effect sizes for correct pronunciations and `r sum(dat$is_mp == 1)+n_outlier_MP` for mispronunciations. Following standard meta-analytic practice, we remove outliers, i.e. effect sizes more than 3 standard deviations from the respective mean effect size. This leads to the exclusion of `r n_outlier_correct` records for correct pronunciations and `r n_outlier_MP` records for mispronunciations.

[Christina: In the above 2 paragraphs I got confused, should it be present or past. I think it switched in the las tparagraph so I started to adapt, but I think it would be best for you to decide. ]

@@

@@

@@

Second, we analyze all of the significant results in the dataset using a p-curve from the p-curve app (v4.0, p-curve.com; @pcurve). This p-curve tests for evidential value by examining whether the p-values follow the expected distribution of a right skew in case the alternative hypothesis is true, versus a flat distribution that speaks for no effect being present in the population and all observed significant effects being spurious. 
Responses to correctly pronounced and mispronounced labels are predicted to show different patterns of looking behavior. In other words, there is an expectation that infants should look to the target when hearing a correct pronunciation, but studies vary in their report of significant looks to the target when hearing a mispronounced label (i.e. there might be no effect present in the population, see e.g., ); as a result, we conduct these two analyses to assess publication bias separately for both conditions.

@@

[Chrisitna: If you add prisma, then this is figure 2]

@@

We should also point out that funnel plot asymmetry can be caused by multiple factors beside publication bias, such as heterogeneity in the data. There are various possible sources of heterogeneity, which our subsequent moderator analyses will begin to address. Nonetheless, we will remain cautious in our interpretation of our findings and hope that an open dataset which can be expanded by the community will attract previously unpublished null results so we can better understand infants' developing mispronunciation sensitivity.

@@

We first calculated the meta-analytic effect for infants' ability to identify objects when hearing correctly pronounced labels. The variance-weighted meta-analytic effect size Hedges' *g* was `r g_SE(sum_eff)` which was significantly different from zero `r CI_p(sum_eff)`. This is a rather large effect size (according to the criteria set by Cohen, 1988; see also Bergmann, et al., 2018; for comparative meta-analytic effect sizes in language acquisition research). That the effect size is significantly above zero suggests that when presented with the correctly pronounced label, infants fixated the corresponding object. Our analysis of funnel plot asymmetry, however, found evidence for publication bias, which might lead to an overestimated effect sizes as smaller, non-significant results might not be published despite the fact that they should occur regularly even in well-powered studies. Although the effect size Hedges' *g* may be overestimated for object identification in response to correctly pronounced words, the p-curve results and a CI lower bound of `r r2(sum_eff$ci.lb)`, which is substantially above zero, together suggest that this result is somewhat robust. In other words, we are confident that the true population mean lies above zero for object recognition of correctly pronounced words.

@@

@@

To evaluate the different predictions we laid out in the introduction for how mispronunciation sensitivity will change as infants develop, we next added the moderator age (centered; continuous and measured in days but transformed into months for ease of interpreting estimates by dividing by 30.44 for Figure 2).

@@

@@

We then examined the interaction between age and mispronunciation sensitivity (correct vs. mispronounced words) in our whole dataset. The moderator test was significant (`r mod_test(rma_MPeffect_age)`). The interaction between age and mispronunciation sensitivity, however, was not significant ($\beta$ `r full_estimate(sum_eff)`); the moderator test was mainly driven by the difference between conditions. The small estimate, as well as inspection of Figure 2 suggests that as infants age, their mispronunciation sensitivity remains the same.

@@

[Christina] Can you try and align the axes for both plots?

@@

dat.cm$Misp_sensitivity <- dat.cm$g_calc.x - dat.cm$g_calc.y
dat.cm$weight <- (dat.cm$weights_g.x + dat.cm$weights_g.y)/2

p.diff <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity)) + 
  ggtitle("b. Mispronunciation Sensitivity")+
  geom_point(aes(size = weight),show.legend=FALSE, alpha = .3) + 
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1), color = "black") +
  scale_colour_manual(values=cbPalette)+
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Hedges' g")

@@

Of the `r n_distinct(dat$short_cite)` papers included in the meta-analysis, `r with(vi2, papers[has_vocab == "vocab"])` analyzed the relationship between vocabulary scores and object recognition for correct pronunciations and mispronunciations (comprehension = `r with(vi1, papers[has_vocab == "comprehension"])` papers and `r with(vi1, count[has_vocab == "comprehension"])` records; production = `r with(vi1, papers[has_vocab == "production"])` papers and `r with(vi1, count[has_vocab == "production"])` records). There is reason to believe that production data are different from comprehension data (the former being easier to estimate for parents in the typical questionnaire-based assessment; Kidd citation), and we therefore planned to analyze these two types of vocabulary measurement separately. However, because only `r with(vi1, papers[has_vocab == "production"])` papers reported correlations with productive vocabulary scores, only limited conclusions that can be drawn. In our vocabulary analysis, we therefore focus exclusively on the relationship between comprehension and mispronunciation sensitivity.

[Christina] So can you not only list papers but also n conditions above? With just 1 paper for production, I wouldn't analyze it to be honest. it's just not enough data. 
I also liked your comments about the time line of this whole thing, can you extract the years of papers which report this? Might be extremely useful in the discussion and strengthens our case that there is no effect, bc people don't find the predicted relation with vocab. 
Also, cann you add a citation for comp vs prod? I think Evan Kidd had a paper on it, if you don't have one handy, I can look it up.
[Katie] I couldn't find what you are referring to. Could you add the Evan Kidd paper? Also, I added a histogram figure below, but I'm not so very sure that it is good enough to add to the paper (its under the heading "Potential Vocabulary Figure"). Let me know what you think.

[Christina] Here is the Kidd paper: https://pure.mpg.de/rest/items/item_2602612_8/component/file_3001229/content Not sur eif it helps.

@@

[Christina] It's significant now!

@@

[Christina] Is there a reason you choose mode and not median? 
[Katie] Hmm, I felt like mode would be interesting, because it gives the most popular choice (74 experimental conditions). But, the median is only 500 ms less, so we could use that too (9 experimental conditions).
[Christina] Oh I get it, maybe if you add that? Whatever you prefer. I was just curious.

[Christina] Would it make sense to present dependent variable first? 
[Katie] I don't have a strong opinion on this. If you think it would be better, then I can change it.
[Christina] Nah, your call.

@@

@@

@@

dat.cm$Misp_sensitivity <- dat.cm$g_calc.x - dat.cm$g_calc.y
dat.cm$weight <- (dat.cm$weights_g.x + dat.cm$weights_g.y)/2

@@

p.AGE <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity, color = post_size)) + 
    #facet_grid(.~post_size)+
  geom_point(aes(size = weight),show.legend=FALSE) +
  labs(title="b")+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1)) +
  scale_colour_manual(values=cbPalette)+
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Misp. Sensitivity")

@@

@@

[Christina] Did I ask the following already: Do we know whether subtrations were on the trial level? Pre vs post is a bit differnt because it loses the individual bias accommodation and the correlation between pre and post on the participant / item level. 
[Katie] You did. I'll put here my answer from before:
From working with Nivi, we did it participants x condition or participants x trial (but mostly the former). But, this is not something we reported in papers. I don't think I read it at all when putting together the dataset for this either.
[Christina] Mention in the discussion that we don't know this and it might be important to establish standard analysis pipelines for MP studies and that we need open data and code? ;)
